Select-based random access \\ to variable-byte encodings

### 2020-04-16 gradu/msc_english_contents.tex
more text2

@@

The $rank$ method is found superior when dataset contains mostly small integers. With larger integers, the decoding needs multiple $rank$ calls and the new $select$-based 
method performs better. Additionally, due to how the data is stored, the proposed $select$ method offers fast access to the next or previous element. This makes a subarray fetch 
very convenient and fast. A solution for subarray fetching and comparison is proposed in this thesis.

@@

It is good to conclude with a summary of findings. You can also use separate chapter for discussion and future work. These details you can negotiate with your supervisor.

@@

 - write conclusions

>>>>

Variable-byte encoding is a method for compressing integers of different byte length. An additional $continuous bit$ is added to the data to denote whether the compressed integer
is continued to the next byte or not. A light-weight data structure is built over the continuous bit array. The fact that the compressed data blocks are of the same size is used
with the data structure to allow direct access to the compressed variable-byte data.

@@

Because of the block reorganizing, the $rank$ does not infact need a $rank$ query when fetching small elements. This makes the $rank$ method superior when dataset contains 
mostly small integers. With larger integers, the decoding needs multiple $rank$ calls and the new $select$-based method performs better.

Additionally, due to how the data is stored, the proposed $select$ method offers fast access to the next or previous element. This makes a subarray fetch 
very convenient and fast. A solution for subarray fetching and comparison is proposed in this thesis.

@@

When the dataset contains mostly small integers, the $rank$ based method by Brisaboa et al. is superior to the proposed $select$ based method. The benefit of using a direct array index instead of a $rank$ 
call for the first block gives a huge advantage. The $rank$ query is also slightly faster than a $select$ query, and therefore the dataset needs to have a large portion of longer elements. This can be seen 
from figure~\ref{graph:data_comparison}.

The order of how data is stored with $select$ compression enables an efficient fetching of a subarray. Only one $select$ query is needed in the beginning, and the decoding of the elements past the first one 
consists of just a few bit operations.

@@
